---
title: "Home Work 4"
author: "Jeff Chandler"
date: "October 20, 2016"
output: html_document
---

#Central Limit Theorem Examples for Normal Distribution
###Set the variables and create the population
```{R}
#set Variables 
PopSize = 500
PopMean = 0
PopStd = 0
SampleSize = 10
SampleSize2=50
SampleMean = 0
SampleStd = 0
#set Mean and std for use with rnorm
m = 8.23
sd = 1.35
SampMeanDist=0
#get normal distribution population
population = rnorm(PopSize, m, sd)

```
### Get the Population Mean and display
```{r}
mean(population)
```
###Get the Standard Deviation and display
```{r}
sd(population)
```
###Create Histogram for Population 
```{r}
hist(population, main = 'Population Distribution', xlab = 'Population', border = 'BLUE', col = 'Purple')
```
###Get 30 samples and create Histogram from population for a size of 10
```{r}
    for(i in 1:30){
      
      SampMeanDist[i] = mean(sample(population,SampleSize, replace = FALSE))
      
    }
    #Create Title
    SampleOneTitle = paste('Sample Mean Distribution ', SampleSize)
    #create histogram
    hist(SampMeanDist, main = SampleOneTitle, xlab = 'Sample Means', col = 'blue', border = 'green')
```
###Get 30 samples and create Histogram from population for a size of 50
```{r}
for(i in 1:30){
      
      SampMeanDist[i] = mean(sample(population,SampleSize2, replace = FALSE))
      
    }
#create title
SampleOneTitle = paste('Sample Mean Distribution ', SampleSize2)
#create histogram
hist(SampMeanDist, main = SampleOneTitle, xlab = 'Sample Means', col = 'blue', border = 'green')
```
#In the following section Is an Example of an Exponential Distribution
###Create the popution 
```{r}
population = rexp(PopSize, rate = .01)
```
###Get the mean and display
```{r}
mean(population)
```

###Get the Standard Deviation and Display
```{r}
sd(population)
```

###Create and display the histogram
```{r}
hist(population, main = 'Population For Exponential Distribution', xlab = 'Population', border = 'BLUE', col = 'Purple')
```
###Get samples and display histogram of distribution with Sample Size of 10
```{r}
for(i in 1:30){
      
      SampMeanDist[i] = mean(sample(population,SampleSize, replace = FALSE))
      
    }
    #Get means
    mean(SampMeanDist)
    #Set histogram title
    SampleOneTitle = paste('Sample Mean Distribution ', SampleSize)
    #create historgram
    hist(SampMeanDist, main = SampleOneTitle, xlab = 'Sample Means', col = 'blue', border = 'green')
```
###Get samples and display histogram of distribution with sample size 50
```{r}
for(i in 1:30){
      
      SampMeanDist[i] = mean(sample(population,SampleSize2, replace = FALSE))
      
    }
    #get means
    mean(SampMeanDist)
    #set title
    SampleOneTitle = paste('Sample Mean Distribution ', SampleSize2)
    #create title
    hist(SampMeanDist, main = SampleOneTitle, xlab = 'Sample Means', col = 'blue', border = 'green')
```